More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-10-23 2016-Weak-FH-Bisim/WeakBisim.tex
Preuve reprise

\end{mathpar}
By using lemma \ref{lem-rel-OT-WOT} we have:
\begin{mathpar}
    \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}
         \implies
\bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T}  \wedge

\openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\bigg)
\end{mathpar}
The (\WTDeux)~ and (\WTTrois)~  rules can be applied repeatedly to produce:
\begin{mathpar}
%\inferrule{
 \forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}          \implies
 \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s=s^1_0 \wedge s^1_{n}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n} \Post_i^1\\
\end{mathpar}
And similarly, a series of $m$ open transitions can be simplified:
\begin{mathpar}
%\inferrule{
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\!\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}       
          \!\implies\!
\openrule
         {
           \set{\gamma_3},\Pred_3, ({x_k\!\gets e_k})^{k\in K}}
         {s_2 \OTWeakarrow {\tau} s'}\! \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s_2=s^3_0 \wedge s^3_{m}\!=s',
\displaystyle{\set{\gamma_3}=\mybigdotcup_{i=0}^{m} \vis{\set{\beta^3_i}}}, 
\Pred_3\!=\!\bigwedge_{i=0}^{m}\Pred^3_i 
%\Post_3= \biguplus_{i=0}^{n_1} \Post_i^1\\
\end{mathpar}
Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} 
\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J^2=J_{x}, (s'^2,t_x|\Pred_{s'^2,t_x})\in \mathcal{R}$; 
 and  \TODO{$\{j\in J^2|\beta_j\neq\tau\}$ useless} \\
 $\Pred \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s'^2,t_x}\subst{\Post^2}\subst{\Post_{OT_x}}\right)$

>>>>

\end{mathpar}
By using lemma \ref{lem-rel-OT-WOT} we have:
\begin{mathpar}
    \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}
         \implies
\bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           {\beta_j^2}^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\bigg)
\end{mathpar}

For the sake of simplicity, a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. By  Definition \ref{def-Weak-bisim} we have for an open transition:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1 \OTarrow {\tau} s'^1} \in \mathcal{T}          
\end{mathpar}
there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,\{j\in J^2|\beta^1_j\neq\tau\}=J_{x}, (s'^1,t_x|\Pred_{s'^1,t_x})\in \mathcal{R}$. \\
 $\Pred_{s1,t} \land \Pred_i^1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s'^1,t_x}\subst{\Post_i^1}\subst{\Post_{OT_x}}\right)$

And similarly, for an open transition:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3 \OTarrow {\tau} s'^3} \in \mathcal{T}          
\end{mathpar}
there exist weak open transition $\symb{WOT}_z^{z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j z}^{j\in J_{z}}, \Pred_{OT_z},\Post_{OT_z}}
         {t'' \OTWeakarrow {\alpha_x} t_z}
\end{mathpar}
 such that  $\forall z,\{j\in J^3|\beta^3_j\neq\tau\}=J_{3}, (s'^3,t_z|\Pred_{s'^3,t_z})\in \mathcal{R}$. \\
 $\Pred_{s^3,t''} \land \Pred_i^3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \left( \forall j\in J_z. \vis{\beta^3_j}=\gamma_{jz}  \Rightarrow \Pred_{OT_z}
     \land \alpha_z\!=\!\tau \land  
     \Pred_{s'^3,t_z}\subst{\Post_i^3}\subst{\Post_{OT_z}}\right)$

Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} 
\end{mathpar}
 there exist weak open transitions $\symb{WOT}_y^{y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_y},\Post_{OT_y}}
         {t' \OTWeakarrow {\alpha_y} t_y}
\end{mathpar}
 such that  $\forall x,\{j\in J^2|\beta^2_j\neq\tau\}=J_{x}, (s'^2,t_y|\Pred_{s'^2,t_y})\in \mathcal{R}$; \\
 $\Pred_{s^2,t'} \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
   \left( \forall j\in J_y. \vis{\beta^2_j}=\gamma_{jy}  \Rightarrow \Pred_{OT_y}
     \land \alpha\!=\!\alpha_y \land  
     \Pred_{s'^2,t_y}\subst{\Post^2}\subst{\Post_{OT_y}}\right)$

On other hand, by applying (\WTTrois)~rule  \TODO{on each  $\symb{WOT}_x$} we have:

 \begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {
\openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\qquad
\openrule
         {
           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_y},\Post_{OT_y}}
         {t' \OTWeakarrow {\alpha_y} t_y}
\qquad
\openrule
         {
           \gamma_{j z}^{j\in J_{z}}, \Pred_{OT_z},({x_k\gets e_k})^{k\in K}}
         {t'' \OTWeakarrow {\tau} t_z}
\\
\Pred=\Pred_{OT_x}\land\Pred_{OT_y}\subst{\Post_{OT_x}}\land (\Pred_{OT_z}\subst{\Post_{OT_y}})\subst{\Post_{OT_x}}
}
{
\openrule
         {
           \gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j y}^{j\in J_{y}}\dotcup\gamma_{j z}^{j\in J_{z}},
		\Pred,
				({x_k\gets (e_k\subst {\Post_{OT_y}})\subst{\Post_{OT_y}}})^{k\in K} } 
         {t \OTWeakarrow {\alpha_x} t_z} 
} 
 \end{mathpar}
 such that $t_x=t' \wedge t_y=t''$

\newpage
-----------------------------------------------------

The (\WTDeux)~ and (\WTTrois)~  rules can be applied repeatedly to produce:
\begin{mathpar}
%\inferrule{
 \forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}          \implies
 \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s=s^1_0 \wedge s^1_{n}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n} \Post_i^1\\
\end{mathpar}
And similarly, a series of $m$ open transitions can be simplified:
\begin{mathpar}
%\inferrule{
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\!\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}       
          \!\implies\!
\openrule
         {
           \set{\gamma_3},\Pred_3, ({x_k\!\gets e_k})^{k\in K}}
         {s_2 \OTWeakarrow {\tau} s'}\! \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s_2=s^3_0 \wedge s^3_{m}\!=s',
\displaystyle{\set{\gamma_3}=\mybigdotcup_{i=0}^{m} \vis{\set{\beta^3_i}}}, 
\Pred_3\!=\!\bigwedge_{i=0}^{m}\Pred^3_i 
%\Post_3= \biguplus_{i=0}^{n_1} \Post_i^1\\
\end{mathpar}
Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} 
\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J^2=J_{x}, (s'^2,t_x|\Pred_{s'^2,t_x})\in \mathcal{R}$; 
 and  \TODO{$\{j\in J^2|\beta_j\neq\tau\}$ useless} \\
 $\Pred \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s'^2,t_x}\subst{\Post^2}\subst{\Post_{OT_x}}\right)$
